Commutative Character Sheaves

### 2015-11-13 followup.tex
Started fixing Lemma 3.4.

\begin{lemma}\label{lem:HH}
If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$. 
\end{lemma}

\begin{proof} 
Define
\begin{align*}
m_2 : G\times G\times G\times G &\to G\times G \\
(x_1,y_1,x_2,y_2) &\mapsto (x_1x_2, y_1y_2) \\
a_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
p_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2)
\end{align*}
and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}), \todo{False, because $m$ is not a group homorphism.}
which comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$. 
This isomorphism satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
By abuse of notation, we will also refer to the missing vertical map down the center of this diagram as $\nu \boxtimes \nu$.  Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so we can reinterpret
\[
\mu : (\cs{L}_2, \mu_2, \nu_2) \to (\cs{L}\boxtimes\cs{L}, \mu \boxtimes \mu, \nu \boxtimes \nu)
\]
as a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
\end{proof}

@@

We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
Conditions \cite{cunningham-roe:13a}*{CS1, CS2, CS3} follow from an adaptation of \cite{cunningham-roe:13a}*{} while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
Condition \eqref{ECS1} is confirmed by brute force.
On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
Condition \cite{cunningham-roe:13a}*{CS4} follows from an adaptation of \cite{cunningham-roe:13a}*{} while condition \eqref{E3} is a consequence of the work above.

@@

Suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
in particular $\gamma = (q\times q)^* \xi$.
Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{H\times H}(G\times G)$.
By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$, completing the proof of Theorem~\ref{thm:Gab}.
This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
\end{proof}

>>>>

\begin{lemma}\label{lem:HH}
If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant Weil local systems on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$. 
\end{lemma}

\begin{proof} 
Define
\begin{align*}
m_2 : G\times G\times G\times G &\to G\times G \\
(x_1,y_1,x_2,y_2) &\mapsto (x_1x_2, y_1y_2) \\
a_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
p_2 : H\times G\times H\times G &\to G\times G \\
(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2)
\end{align*}
and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
The Weil local system $\cs{L}_2$ on $G \times G$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$ defined by ...\todo{Working here.}
This isomorphism satisfies \eqref{E1} and \eqref{E2} as they apply here.
%
Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
\[
\begin{tikzcd}
\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
\end{tikzcd}
\]
By abuse of notation, we will also refer to the missing vertical map down the center of this diagram as $\nu \boxtimes \nu$.  Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
The appropriate version of \eqref{E3} also commutes, so we can reinterpret
\[
\mu : (\cs{L}_2, \mu_2, \nu_2) \to (\cs{L}\boxtimes\cs{L}, \mu \boxtimes \mu, \nu \boxtimes \nu)
\]
as a morphism of equivariant linear character sheaves.
The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.\todo{Add detail here.}
\end{proof}

@@

We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
On objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
Conditions \cite{cunningham-roe:13a}*{CS1, CS2, CS3} follow from an adaptation of \cite{cunningham-roe:13a}*{} while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
Condition \eqref{ECS1} is confirmed by brute force.
On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
Condition \cite{cunningham-roe:13a}*{CS4} follows from an adaptation of \cite{cunningham-roe:13a}*{} while condition \eqref{E3} is a consequence of the work above.

@@

Suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
in particular $\gamma = (q\times q)^* \xi$.
Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\Loc_{H\times H}(G\times G)$.
By Lemma~\ref{lem:torsor}, this corresponds uniquely to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$, completing the proof of Theorem~\ref{thm:Gab}.
This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
\end{proof}
